Transparency or Opacity? A Critical Examination of Public Access to Information in Romania's Local Administration

### 2023-06-22 Article.Rmd
methodology v1

# Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

## Procedure

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.

# Results
```{r Analysis, echo=F, include=F}
  source("01 - Analysis.R")
```
# Contingency analysis based on the rank of the locality
```{r Range, echo=F}
  # Item 1
  chi.1 <- round(chi.R.I1$statistic, 2);  df.chi.1 <- chi.R.I1$parameter; p.chi.1 <- chi.R.I1$p.value
  mun.n.1 <- R.I.1.prop[1,1]; mun.y.1 <- R.I.1.prop[2,1]
  cit.n.1 <- R.I.1.prop[1,2]; cit.y.1 <- R.I.1.prop[2,2]
  vil.n.1 <- R.I.1.prop[1,3]; vil.y.1 <- R.I.1.prop[2,3]

>>>>

# Methodology

## Research objectives

O1: To assess the transparency and accessibility of public interest information available on the official websites of selected administrative-territorial units in Romania.

O2: To identify patterns or correlations, if any, between the rank of the administrative-territorial units and the availability of public interest information on their websites.

## Data collection

For data collection, we visited the official websites of 126 administrative-territorial units in Romania, selecting three from each county based on a ranking criterion: 1 - the county seat municipality, typically the largest locality in the county; 2 - a town, generally the second or third largest in the county; 3 - a commune, specifically the one with the highest number of inhabitants.

Subsequently, we pursued the presence of the following official documents or public interest information:

Item 1 - Normative acts regulating the organization and operation of the authority or public institution
Item 2 - Organizational structure, responsibilities of the departments, operation program, public audience program of the authority or institution
Item 3 - Names and surnames of the leaders of the authority or institution and of the officer responsible for disseminating public information
Item 4 - Contact details of the authority or institution, namely: name, headquarters, phone numbers, fax, email address, and website address
Item 5 - Financial sources, budget, and balance sheet
Item 6 - The authority's or institution's own programs and strategies
Item 7 - A list encompassing the documents of public interest
Item 8 - A list containing the categories of documents produced and/or managed, according to the law
Item 9 - The methods of challenging the decision of the authority or institution when a person feels aggrieved regarding the right to access the requested public interest information
Item 10 - Declarations of wealth and interests
Item 11 - Council resolutions
Item 12 - Public procurement contracts
Item 13 - Public interest announcements

The presence or absence of these elements on the websites of the administrative-territorial units was coded as "Yes" or "No", respectively.

## Data analysis
In the data analysis phase of this study, we utilized a systematic and statistical approach to identify relationships and patterns among the dataset variables.

We primarily employed the Chi-squared test, a statistical hypothesis test that determines whether there is a significant association between two categorical variables. In our case, these variables were the rank of the administrative-territorial units and the availability of each item of public interest information.

We used `r cite_r("r-references.bib")` for all our analyses.

# Results
```{r Analysis, echo=F, include=F}
  source("01 - Analysis.R")
```

```{r Range, echo=F}
  # Item 1
  chi.1 <- round(chi.R.I1$statistic, 2);  df.chi.1 <- chi.R.I1$parameter; p.chi.1 <- chi.R.I1$p.value
  mun.n.1 <- R.I.1.prop[1,1]; mun.y.1 <- R.I.1.prop[2,1]
  cit.n.1 <- R.I.1.prop[1,2]; cit.y.1 <- R.I.1.prop[2,2]
  vil.n.1 <- R.I.1.prop[1,3]; vil.y.1 <- R.I.1.prop[2,3]
